---
title: "Daniel_Johnson_HW_12"
author: "Daniel Johnson"
date: "November 30, 2018"
output: pdf_document
---
#API Search Functions
Function to produce the base url with domain and a keyword to search by
```{r}
get_base <- function(api, keyword){
  base <- "https://newsapi.org/v2/everything?"
  domain <- "domains=elmundo.es"
  query <- paste("q=", keyword, sep="")
  
  url <- paste(base, domain, sep = "")
  url <- paste(url, query, sep="&")
  url <- paste(url, api, sep="&apiKey=")
  url <- paste(url, "100", sep="&pageSize=")
  
  return(url)
  
}

get_base("03c2de1a4d92413f984dd51bf0f98b64", "messi")
```

Function to get all the articles returned for a given keyword
```{r}
get_article_keyword <- function(api, keyword){
  url <- get_base(api, keyword)
  
  df <- httr::GET(url=url)
  df <- jsonlite::fromJSON(rawToChar(df$content))
  articles <- df$articles
  
  articles <- articles$content
  
  return(articles)
}

head(get_article_keyword("03c2de1a4d92413f984dd51bf0f98b64", "messi"))
```

Function to get all the articles for a given keyword on a given date
```{r}
get_word_dates <- function(api, keyword, date){
  url <- get_base(api, keyword)
  url <- paste(url, date, sep="&from=")
  url <- paste(url, date, sep="&to=")
  
  df <- httr::GET(url=url)
  df <- jsonlite::fromJSON(rawToChar(df$content))
  
  articles <- df$articles
  articles <- articles$content
  return(articles)
}

head(get_word_dates("03c2de1a4d92413f984dd51bf0f98b64", "trump", "2018-11-29"))
```

Function that returns the number of articles written on a given topic 
```{r}
get_narticles <- function(api, keyword){
  url <- get_base(api, keyword)
  
  df <- httr::GET(url=url)
  df <- jsonlite::fromJSON(rawToChar(df$content))
  
  nresults <- df$totalResults
  return(nresults)
}

get_narticles("03c2de1a4d92413f984dd51bf0f98b64", "trump")
```

Function that gives you all the articles written on a given day 
```{r}
get_articles_dates <- function(api, date){
  base <- "https://newsapi.org/v2/everything?"
  domain <- "domains=elmundo.es"
  
  url <- paste(base, domain, sep = "")
  url <- paste(url, date, sep="&from=")
  url <- paste(url, date, sep="&to=")
  url <- paste(url, api, sep="&apiKey=")
  url <- paste(url, "100", sep="&pageSize=")
  
  df <- httr::GET(url=url)
  df <- jsonlite::fromJSON(rawToChar(df$content))
  
  articles <- df$articles
  articles <- articles$content
  return(articles)
}

head(get_articles_dates("03c2de1a4d92413f984dd51bf0f98b64", "2018-11-29"))
```
Function for all the headlines returned for a given search word
```{r}
get_headline_keyword <- function(api, keyword){
  url <- get_base(api, keyword)
  
  df <- httr::GET(url=url)
  df <- jsonlite::fromJSON(rawToChar(df$content))
  articles <- df$articles
  
  articles <- articles$title
  
  return(articles)
}

head(get_headline_keyword("03c2de1a4d92413f984dd51bf0f98b64", "messi"))
```

Function for all of the headlines on a given date 
```{r}
get_headlines_dates <- function(api, date){
  base <- "https://newsapi.org/v2/everything?"
  domain <- "domains=elmundo.es"
  
  url <- paste(base, domain, sep = "")
  url <- paste(url, date, sep="&from=")
  url <- paste(url, date, sep="&to=")
  url <- paste(url, api, sep="&apiKey=")
  url <- paste(url, "100", sep="&pageSize=")
  
  df <- httr::GET(url=url)
  df <- jsonlite::fromJSON(rawToChar(df$content))
  
  articles <- df$articles
  articles <- articles$title
  return(articles)
}

head(get_headlines_dates("03c2de1a4d92413f984dd51bf0f98b64", "2018-11-29"))
```

#Google Translate Functions
##Actual translation function 
###Spanish to English
```{r}
get_translated <- function(text, api){

source <- "es"
target <- "en"
news <- text

body <- paste("{",
              "'q':'", news, "',", 
              "'source':'", source, "',",
              "'target':'", target, "',",
              "'format':'text',",  
              "}", sep="")

base <- "https://translation.googleapis.com/language/translate/v2?key="
url <- paste(base, api, sep="")

x <- httr::POST(url, body = body)
x <- jsonlite::fromJSON(rawToChar(x$content))

out <- x$data$translations$translatedText

return(out)
}

text <- get_article_keyword("03c2de1a4d92413f984dd51bf0f98b64", "trump")
text <- text[10]
get_translated(text, "AIzaSyDXaGrD6yGkK3kRnYPp_4s-dQ2DkLnCXlE")
```

##Text to speech function
```{r}
get_spoken <- function(text, api){
  text <- paste(text, collapse=" ")
  
  input <- paste("'input':{'text':'", text, "'}", sep="")
  voice <- "'voice':{'languageCode':'nl-NL','name':'nl-NL-Standard-A','ssmlGender':'FEMALE'}"
  output <- "'audioConfig':{'audioEncoding':'MP3'}"
  
  s_body <- paste("{", input, ",", voice, ",", output, "}", sep="")
  
  base_url <- "https://texttospeech.googleapis.com/v1/text:synthesize?key="
  url <- paste(base_url, api, sep="")
  
  x <- httr::POST(url, body = s_body)
  x <- jsonlite::fromJSON(rawToChar(x$content))
  x <- x$audioContent
  
  shell("del translated.txt")
  con <- file("translated.txt", "w")
  writeLines(x, con=con)
  close(con)
  
  shell("del trans_audio.mp3")
  shell("certutil -decode translated.txt trans_audio.mp3")
  shell("start trans_audio.mp3")
}
```
