---
title: "新华网－XinHua.net"
author: "Samuel Joslin"
date: "12/1/2018"
header-includes:
  - \usepackage{ctex}
output: 
  pdf_document:
    latex_engine: xelatex
---
---

**新华网 or XinHua.net is an popular news outlet in China. My goal is to create a number of functions to allow users to interact with headlines on XinHua.net**


In order to user all the functions, users will need to aquire a unique XinHua.net API Key and a GoogleCloud API key. Below I include mine for demonstration purposes.

```{r, message=FALSE}
library(httr, quietly = T)
library(dplyr, quietly = T)
library(lubridate, quietly = T)
library(base64, quietly = T)

samAPIkey <- "8665b12062004f058c454ea7c4b2bd9a"
googleAPI_key <- "AIzaSyCOrcUDCTzVLfCgTekyFYhT_S4hJthGyak"

```


The user can defiine their API as a global vairable to make using the functions easier. This way, the user's will simply need to input the variable name into the functions, rather than enter their entire key everytime. 



**getHeadlines_TimeSpan**

The getHeadlines_TimeSpan function takes a beginning date and end date. It returns all the headlines posted by XinHua in between those dates. Its important to note date1 must be earlier than date2. 

```{r}
getHeadlines_TimeSpan <- function(date1,date2, APIkey){
  base <- "https://newsapi.org/v2/everything?"
  sources <- "xinhua-net"
  url1 <- paste(base,"sources=",sources,"&","from=",date1,"&","to=",date2,"&sortBy=popularity&","apiKey=",
                APIkey, sep = "")

  x <- httr::GET(url=url1)
  x <- jsonlite::fromJSON(rawToChar(x$content))
  return(x$articles$title)
}
```

**getHeadlines_TimeSpan-- Example**
```{r}
head(getHeadlines_TimeSpan(2018-11-19,2018-11-20, samAPIkey))
```



**getHeadlines_keyword**

The getHeadlines_keyword function accepts a keyword as a character vector to search by and returns the headlines regarding the input word.

```{r}
getHeadlines_keyword <- function(keyword, APIkey){
  base <- "https://newsapi.org/v2/everything?"
  sources <- "xinhua-net"
  url1 <- paste(base,"sources=",sources,"&","q=",keyword,
                "&sortBy=popularity&","apiKey=",
                APIkey, sep = "")
  x <- httr::GET(url=url1)
  x <- jsonlite::fromJSON(rawToChar(x$content))
  return(x$articles$title)
}
```


**getHeadlines_keyword-- Example**


```{r}
head(getHeadlines_keyword("美国",samAPIkey))
```


**Chinese to English Headline Translation**

This function takes a vector of chinese characters and returns a data.frame where the first column is the input and the second column is the translation. 


```{r}
chinese_to_en_translator <- function(headlines,gAPI_key){
  nh <- length(headlines)
  en_trans <- rep(NA,nh)
  for (i in 1:nh){
    ch <- headlines[i]
    source <- "zh"
    target <- "en"
    body <- paste("{",
                  "'q':'", ch, "',",
                  "'source':'", source, "',",
                  "'target':'", target, "',",
                  "'format':'text'",  
                  "}", sep="")
    
    base <- "https://translation.googleapis.com/language/translate/v2?key="
    url <- paste(base, gAPI_key, sep="")
    
    x <- httr::POST(url, body = body)
    x <- jsonlite::fromJSON(rawToChar(x$content))
    en_trans[i] <- x$data$translations$translatedText
    
  }
  return(data.frame(Original = headlines, Translation = en_trans))
}


```

**Chinese to English Headline Translation-- Example**

```{r,fig.align="left"}
chinese_headlines <- head(getHeadlines_keyword("美国",samAPIkey))
print(chinese_to_en_translator(chinese_headlines,googleAPI_key), right =F)
```




**Text to Speech**

The text_to_speech function takes a character string and dictates it. 

```{r}
text_to_speech  <-function(text, gAPIkey){

  text  <-paste(text,collapse="  ")
  text  <-gsub("'","",  text)
  
  input  <-paste("'input':{'text':'",  text,"'}",sep="")
  voice  <-"'voice':{'languageCode':'en-GB','name':'en-GB-Standard-C','ssmlGender':'FEMALE'}"
  output  <-"'audioConfig':{'audioEncoding':'MP3'}"
  
  s_body  <-paste("{",  input,",",  voice,",",  output,"}",sep="")
  base_url <- "https://texttospeech.googleapis.com/v1/text:synthesize?key="
  base_url  <-url  <-paste(base_url,gAPIkey,sep="")
  
  x  <-httr::POST(url,body  =s_body)
  x  <-jsonlite::fromJSON(rawToChar(x$content))

  Sys.setenv(output_string=x$audioContent)
  
  system("echo $output_string > sound_out.txt")
  system("base64 --decode sound_out.txt > sound_out.mp3")
  system("afplay sound_out.mp3")
}
```

**text_to_speech-- example**

```{r}
chinese_headlines <- head(getHeadlines_keyword("美国",samAPIkey))
text_to_speech(chinese_headlines[1],googleAPI_key)
```